$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-04 paper/paper.tex
Write on Thiemann's paper

This work is heavily based on the work by Allais \cite{Allais2018a}.
Allais uses leftover typing to build a bidirectional type system for the linear \lambdacalc{}.
He proves type preservation and provides a decision procedure for type checking and type inference.
He then goes on showing the soundness and completeness with respect to the sequent calculus for intuitionistic linear logic.
Also extrinsic.
Also in Agda.
Also de Bruijn.
We apply this to the \picalc{}.
We generalise the usage algebra.
Our type system is not bidirectional --- scope restriction needs usage annotations.
Adding bidirectionality would provide us with a decision procedure for type checking.

\cite{Thiemann2019}
intrinsicly typed
linear session types with recursion and subtyping.
also in Agda.
Also de Bruijn.
semantics as an intrinsically typed CEK machine
explicit context splits
MicroSession, minimal GV, lambda calculus with session types
contexts remove elements with multiplicity 0
keeps a global session context

@@

\cite{LTS-semantics}

@@

>>>>

Leftover typing as presented in this paper is based on work by Allais \cite{Allais2018a}.
Allais uses leftover typing to mechanise in Agda a bidirectional type system for the linear \lambdacalc{}.
This type system sits on top of an untyped but well-scoped syntax with de Bruijn indices.
He proves type preservation and provides a decision procedure for type checking and type inference.
In this paper, we apply his technique to the \picalc{}, but limit ourselves to type-checking (scope restriction needs usage annotations) terms, and focus on generalising the usage algebra.

Taking an intrinsic approach, Thiemann formalises in Agda the MicroSession (minimal GV \cite{}) calculus with support for recursion and subtyping \cite{Thiemann2019}.
Context splits are given extrinsically, and exhausted elements are removed from typing contexts altogether.
The semantics are given as an intrinsically typed CEK machine with a global context of session-typed channels.

@@

@@

Adding bidirectionality would provide us with a decision procedure for type checking.
